Untitled

### 2023-08-14 code/analysis_Redo.Rmd
split chunks

did2s(
      data = df.sum ,#%>% filter(ZipFilter == 2), 
      yname = "Sites", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom) %>% 
  filter(Year %in% c(2015, 2019)) %>% 
  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = avgdist) %>% 
  mutate(ds = `2019` - `2015`) %>% 
    ungroup() %>% 
    mutate(filt = ifelse(ds > quantile(ds, 0.5, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(filt == 1),#%>% filter(ZipFilter == 2), 
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom), by = c("Grant Number","Year")) ,#%>% filter(ZipFilter == 2), 
      yname = "Altmans.Z", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(avgdist / 10) + I(Tx *as.numeric(avgdist / 10)),
        cluster_var = "ID",
      verbose = FALSE
    )

#select(ID, Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z) %>% left_join(df.qual.exp %>% select(ID, Year, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("ID","Year"))
out.qual <- event_study(data = df.qual.exp,# %>% filter(ZipFilter == 2), 
  yname = "Altmans.Z", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM)

@@

>>>>

did2s(
      data = df.sum , 
      yname = "Altmans.Z", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

#select(ID, Year, ZipFilter, ID, Att, Sites, Qcomp, Altmans.Z) %>% left_join(df.qual.exp %>% select(ID, Year, Pct.NHA:Pct.Children, MCD, COM, MCR), by = c("ID","Year"))
out.qual <- event_study(data = df.qual.exp %>% filter(ZipFilter == 1), 
  yname = "Altmans.Z", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM)

@@

## Variations

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom) %>% 
  filter(Year %in% c(2015, 2019)) %>% 
  pivot_wider(id_cols = `Grant Number`, names_from = Year, values_from = avgdist) %>% 
  mutate(ds = `2019` - `2015`) %>% 
    ungroup() %>% 
    mutate(filt = ifelse(ds > median(ds, na.rm = TRUE), 1, 0)), by = c("Grant Number")) %>% filter(filt == 0),#%>% filter(ZipFilter == 2), 
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

did2s(
      data = df.sum %>% left_join(df.spill2 %>% 
  group_by(`Grant Number`, Year) %>% 
  summarise(num = sum((Dist + 1) * Sites), 
         denom = sum(Sites), 
         avgdist = num / denom) %>% 
    filter(Year == 2016) %>% select(`Grant Number`, avgdist), by = c("Grant Number")) ,#%>% filter(ZipFilter == 2), 
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(avgdist / 10) + I(Tx *as.numeric(avgdist / 10)),
        cluster_var = "ID",
      verbose = FALSE
    )
